---
title: "CLT - Central Limit Theorem"
author: "Erica Brooks"
date: "2023-05-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# For Live Session Assignment 1
## CLT


#Questions 2a and 2b Generate a population of 10,000,000 from a chi-square distribution with 2 degrees of freedom. Use rchisq() function. Histogram of the population displaying the right skewness

```{r}
x <- rchisq(10000000, df = 2)

hist(x, freq = FALSE, xlim = c(0, 20), ylim = c(0, 0.2))

curve(dchisq(x, df = 2), from = 0, to = 19, 
      n = 5000, col= 'pink', lwd=2, add = T)
```

#Question 2c - Mean and Standard Deviation of the population
```{r}
mean(x) #mean of population
sd(x) #population variance

```
#Question 2e - 10,000 means of size 50. Set the parameters

```{r}
n1 = 50 # sample size per sample for 1st distribution
simulations = 10000 #number of samples and thus number of xbars we will generate.  
mu = 0 # mean parameter for use with normal distributions
sigma = 1 # standard deviation parameter for use with normal distributions
```

#Data Holder

```{r}
xbar_holder1 = numeric(simulations) # This will hold all the sample means for the distribution.

```

#Simulate and Store. Generate 10,000 samples each of size 50 and find the mean of each sample. Then store each mean in the xbar_holder vector.

```{r}
for (i in 1:simulations)
{ 
  sample1 = rnorm(n1,mean = mu, sd = sigma)
  xbar1 = mean(sample1)
  xbar_holder1[i] = xbar1
}
```

#Display the distribution of sample means (plot a histogram of the sample means)
```{r}
par(mfrow = c(2,1))
hist(xbar_holder1, col = "pink", main = paste("Distribution of the sample mean: n = ", n1), xlab = "Dist Sample Means", xlim = c(-4,4))

```

#Question 2f - Summary statistics of the distribution of the simulated sample means. 
```{r}
mean(xbar_holder1) #number summary and the mean
sd(xbar_holder1) # standard deviation of distribution

```


